\documentclass[runningheads]{llncs}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{subcaption}

\usepackage[commandnameprefix=always, defaultcolor=red]{changes}  %使用changes宏包
% \usepackage[final]{changes} %禁用修订，输出最终修订完成的版本
\definechangesauthor[name={zheliku}, color=blue]{zheliku} %修订作者

\bibliographystyle{splncs04}

\AtBeginDocument{%
  \providecommand\BibTeX{{%
    Bib\TeX}}}

\begin{document}

\title{VRTI: Providing Realistic Haptic Feedback and Hand Manipulation for Immersive Physics Learning}

% \author{Hailin Ji\inst{1} \and 
% % \orcidID{0009-0002-3512-6730} 
% Yihang Li\inst{1} \and 
% Yiran Zhang\inst{1} \and 
% Hongwen Zhang\inst{1} \and 
% Xiaoyan Hu\inst{1} \and 
% Yanhong Luo\inst{2}}
 
% \authorrunning{H. Ji et al.}

% \institute{Beijing Normal University, Beijing, China \and
% Northwest Minzu University, Beijing, China}

\author{Anonymous Author(s)}

\maketitle

\begin{abstract}
As gesture tracking technology matures, VR-based immersive learning environments enable Gesture Interaction (GI) with virtual objects, offering intuitive educational experiences. However, the absence of haptic feedback in GI compromises immersion. 
\chadded[id=zheliku]{
  This paper proposes Virtual-Real Twin Interaction (VRTI), which synchronizes Virtual Interactive Objects (VIO) with Real Interactive Objects (RIO) to provide dynamic haptic feedback for gestures. Key innovations include: 
  1) \textbf{Dynamization of props' haptics}: Real-time sensor networks transform physical props' static properties into dynamic feedback through spatiotemporal synchronization. 
  2) \textbf{Gesture-props consistency model}: Achieves visuo-haptic synchronized interaction, and supports interaction calibration during hand manipulations.
  Applied to high school momentum conservation experiments, three VR twins (puller/button/knob) support grasping, pressing, and pinching. Controlled trials (VRTI: N=32 vs GI: N=32) demonstrate that VRTI: 1) Significantly enhanced motivation (p<0.001) and immersion (p<0.001). 2) Reduced extraneous cognitive load (p<0.001, |r|=0.625). 3) higher experimental understanding (p=0.05) and better comprehension application (p=0.005)
}

\keywords{Virtual-Real Twin Interaction \and Virtual Reality \and Haptic Feedback \and Physics Prop \and Immersive Physics Learning \and Gesture Interaction}
\end{abstract}

\input{1_introduction.tex}
\input{2_related_work.tex}
\input{3_method.tex}
\input{4_VRTI_design.tex}
\input{5_experiment_and_evaluation.tex}
\input{6_limitations_and_futurework.tex}
\input{7_conclusion.tex}

\begin{credits}
\subsubsection{\ackname} 
This study was supported by the Natural Science Foundation of China (No.62377004).

\subsubsection{\discintname}
The authors declare no competing interests.
\end{credits}


\bibliography{VRTI-bib}

\end{document}